---
title: "Analysis"
output: html_document
date: "2025-05-24"
---

This script is to re-create the analysis for the following manuscript:

**Title** The paradoxical impact of drought on West Nile virus risk: insights from long-term ecological data

*Authors* S Sambado*, T J Sipin, Z Rennie, A Larsen, J Cunningham, A Quandt, D Sousa, A J MacDonald

*corresponding author: sbsambado-at-ucsb.edu / ssambado-at-stanford.edu

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## upload necessary packages
library(fixest)
library(sandwich)
library(broom)


## upload necessary data
# mosquito abundances full
abund_tar_full <- read.csv("data/abund_tar_full_clean.csv") %>% dplyr::select(-X)
abund_quin_full <- read.csv("data/abund_quinq_full_clean.csv") %>% dplyr::select(-X)

# panel data for abundances
abund_tar_panel <- read.csv("data/abund_tar_panel_clean.csv") %>% dplyr::select(-X)
abund_quin_panel <- read.csv("data/abund_quin_panel_clean.csv") %>% dplyr::select(-X)
# panel data for wnv mir 
wnv_tar_panel <- read.csv("data/wnvmir_tar_panel_clean.csv")  %>% dplyr::select(-X)
wnv_quin_panel <- read.csv("data/wnvmir_quin_panel_clean.csv")  %>% dplyr::select(-X)

# covariate information
trap_station <- read.csv("data/trapstation_info_clean.csv") %>% dplyr::select(-X)
arbonet_human <- read.csv("data/arbonet_ca_clean.csv")
```


#Main Text

##Abstract
```{r}
## total trap nights
abund_tar_full %>% 
  filter(month > 3 & month < 11) %>% # filter to peak mosquito months
  summarise(total = sum(trap_nights, na.rm = TRUE)) # 528,627	

abund_quin_full %>%
  filter(month > 3 & month < 11) %>% # filter to peak mosquito months
  summarise(total = sum(trap_nights, na.rm = TRUE)) # 528,627	

## total years
range(abund_tar_full$year) # 2010 2023
range(abund_quin_full$year) # 2010 2023
```


##Introduction & Methods
```{r}
## total trap stations
length(unique(trap_station$id)) # 278

## total mosquitos
abund_tar_full %>% 
  filter(month > 3 & month < 11) %>% # filter to peak mosquito months
  summarise(total = sum(total_mosquitoes, na.rm = TRUE)) # 2,353,573	

abund_quin_full %>% 
  filter(month > 3 & month < 11) %>% # filter to peak mosquito months
  summarise(total = sum(total_mosquitoes, na.rm = TRUE)) # 1,321,196

2353573 + 1321196	 # 3,674,769

## total cluster ID
length(unique(trap_station$clust)) # 96
```


##Results

###Summary
```{r}
## total mosquitos
abund_tar_full %>% 
  filter(month > 3 & month < 11) %>% # filter to peak mosquito months
  summarise(total = sum(total_mosquitoes, na.rm = TRUE), # 2,353,573	
            mean_trapnight = round(mean(mos_per_trap_night, na.rm = TRUE),1), # 14
            sd_trapnight = round(sd(mos_per_trap_night, na.rm = TRUE),1)) # 82.1	

abund_quin_full %>% 
  filter(month > 3 & month < 11) %>% # filter to peak mosquito months
  summarise(total = sum(total_mosquitoes, na.rm = TRUE), # 1,321,196	
            mean_trapnight = round(mean(mos_per_trap_night, na.rm = TRUE),1), # 9.3
            sd_trapnight = round(sd(mos_per_trap_night, na.rm = TRUE),1)) #35



## WNV
wnv_tar_panel  %>% 
  filter(month != "March") %>% # filter to peak mosquito months
  summarise(mean_mir = round(mean(mir, na.rm = TRUE),1), # 3.2
            sd_mir = round(sd(mir, na.rm = TRUE), 1)) # 9.5

wnv_quin_panel  %>% 
  filter(month != "March") %>% # filter to peak mosquito months
  summarise(mean_mir = round(mean(mir, na.rm = TRUE),1), # 4.1
            sd_mir = round(sd(mir, na.rm = TRUE), 1)) # 10.5
```

###Panel models

Check distribution of outcomes
```{r}
# ### UNTRANSFORMED
# 
# ## ABUNDANCE
# hist(abund_tar_panel$mos_per_trap_night) # skewed
# range(abund_tar_panel$mos_per_trap_night, na.rm = TRUE) # 0 2464 (includes 0)
# 
# hist(abund_quin_panel$mos_per_trap_night) # skewed
# range(abund_quin_panel$mos_per_trap_night, na.rm = TRUE) # 0 1124.5 (includes 0)
# 
# 
# ## WNV MIR
# hist(wnv_tar_panel$mir) # skewed
# range(wnv_tar_panel$mir, na.rm = TRUE) # 0 83.3333 (includes 0)
# 
# hist(wnv_quin_panel$mir) # skewed
# range(wnv_quin_panel$mir, na.rm = TRUE) # 0 142.8571 (includes 0)
# 
# 
# ### TRANSFORMED
# ## ABUNDANCE
# hist(log(abund_tar_panel$mos_per_trap_night+1)) # better but still skewed
# range(log(abund_tar_panel$mos_per_trap_night+1), na.rm = TRUE) # 0 7.809947 (includes 0)
# 
# hist(log(abund_quin_panel$mos_per_trap_night+1)) # better but still skewed
# range(log(abund_quin_panel$mos_per_trap_night+1), na.rm = TRUE) # 0 7.025983 (includes 0)
# 
# 
# ## WNV MIR
# hist(log(wnv_tar_panel$mir+1)) # skewed
# range(log(wnv_tar_panel$mir+1), na.rm = TRUE) # 0 4.434777 (includes 0)
# 
# hist(log(wnv_quin_panel$mir+1)) # skewed
# range(log(wnv_quin_panel$mir+1), na.rm = TRUE) # 4.968821
```

Model construction
```{r}
## ABUNDANCE
# Cx. tarsalis
mod_abund_tar <- feols(log(mos_per_trap_night + 1) ~ # log transformed better fit, 0s in data so add 1
                         pdsi_standardized_lag_1month + # primary covariate of interest
                         woy_cms_mean_standardized | # control
                         clust + month, # fixed-effects dummy variables
                       vcov = "conley", # specify conley standard errors
                       data = abund_tar_panel) # data in panel format

# Cx. quinquefasciatus
mod_abund_quin <- feols(log(mos_per_trap_night + 1) ~ # log transformed better fit, 0s in data so add 1
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         clust + month,
                      # specify conley standard errors  
                       vcov = "conley",
                       data = abund_quin_panel)


## WNV MIR
# Cx. tarsalis
mod_wnv_tar <- feols(log(mir + 1) ~ # log transformed better fit, 0s in data so add 1
                       pdsi_standardized_lag_1month + 
                       woy_cms_mean_standardized + 
                       mean_competence_standardized |
                       clust + month,
                     # specify conley standard errors
                       vcov = "conley",
                       data = wnv_tar_panel)

# Cx. quinquefasciatus
mod_wnv_quin <- feols(log(mir + 1) ~ # log transformed better fit, 0s in data so add 1
                       pdsi_standardized_lag_1month + 
                       woy_cms_mean_standardized + 
                       mean_competence_standardized |
                       clust + month,
                     # specify conley standard errors
                       vcov = "conley",
                       data = wnv_quin_panel)

```

Model summaries
```{r}
## abundance models
summary(mod_abund_tar) # Cx. tarsalis result
summary(mod_abund_quin) # Cx. quinquefasciatus result

## wnv mir models
summary(mod_wnv_tar) # Cx. tarsalis result
summary(mod_wnv_quin) # Cx. quinquefasciatus result
```

#Tables

##Table 1

Mosquito surveillance
```{r}
## abundances

# Cx. tarsalis
abund_tar_panel %>% 
  # calculate yearly mean and sd of mos per trap night
  group_by(year) %>% 
  summarise(mean = mean(mos_per_trap_night, na.rm = TRUE),
            sd = sd(mos_per_trap_night, na.rm = TRUE)) %>%
  # round values
  mutate(mean = round(mean,1),
         sd = round(sd,0))

# Cx. quinquefasciatus
abund_quin_panel %>% 
  # calculate yearly mean and sd of mos per trap night
  group_by(year) %>% 
  summarise(mean = mean(mos_per_trap_night, na.rm = TRUE),
            sd = sd(mos_per_trap_night, na.rm = TRUE)) %>% 
  mutate(mean = round(mean,1),
         sd = round(sd,0))

## wnv mir 

# Cx. tarsalis
wnv_tar_panel %>% 
  # calculate yearly mean and sd of wnv mir
  group_by(year) %>% 
  summarise(mean = mean(mir, na.rm = TRUE),
            sd = sd(mir, na.rm = TRUE)) %>% 
  mutate(mean = round(mean,1),
         sd = round(sd,0))

# Cx. quinquefasciatus
wnv_quin_panel %>% 
  # calculate yearly mean and sd of wnv mir
  group_by(year) %>% 
  summarise(mean = mean(mir, na.rm = TRUE),
            sd = sd(mir, na.rm = TRUE)) %>% 
  mutate(mean = round(mean,1),
         sd = round(sd,0))
```

Human WNV incidence
```{r}
arbonet_human %>% 
  rename(GEOID = county) %>% 
  mutate(GEOID = str_pad(GEOID, width = 5, pad = 0), # make sure FIPS are 5 characters
         GEOID = as.character(GEOID)) %>% 
  filter(GEOID == "06029") %>%  # filter for Kern County
  arrange(year) %>% # descend year order
  # calculate incidence per 100,000 people
  mutate(incidence = (reported_human_cases/909235)*100000, # pop based on 2020 Census in Kern
         incidence = round(incidence,2))%>% # round
  dplyr::select(year, incidence)
```


##Table 2
```{r}
# same as model summaries above
## abundance models
summary(mod_abund_tar) # Cx. tarsalis result
summary(mod_abund_quin) # Cx. quinquefasciatus result

## wnv mir models
summary(mod_wnv_tar) # Cx. tarsalis result
summary(mod_wnv_quin) # Cx. quinquefasciatus result
```


#Supporting Information

##Table S1
NA

##Table S2
NA

###Table S3
Model summaries for Cx. tarsalis abundance. 
```{r}
## TARSALIS
mod_abund_tar_re_none <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized, 
                       
                       vcov = "conley",
                       data = abund_tar_panel)


mod_abund_tar_re_clust <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         clust,
                       
                       vcov = "conley",
                       data = abund_tar_panel)

mod_abund_tar_re_month <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         month,
                       
                       vcov = "conley",
                       data = abund_tar_panel)


mod_abund_tar_re_year <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         year,
                       
                       vcov = "conley",
                       data = abund_tar_panel)

mod_abund_tar_re_clustmonth <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         clust + month,
                       
                       vcov = "conley",
                       data = abund_tar_panel)


mod_abund_tar_re_clustmonthyear <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         clust + month + year,
                       
                       vcov = "conley",
                       data = abund_tar_panel)



## full summaries
summary(mod_abund_tar_re_none)
summary(mod_abund_tar_re_clust)
summary(mod_abund_tar_re_month)
summary(mod_abund_tar_re_year)
summary(mod_abund_tar_re_clustmonth)
summary(mod_abund_tar_re_clustmonthyear)


## tidy summaries for supplemental table
tidy(mod_abund_tar_re_none) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_tar_re_clust) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_tar_re_month) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_tar_re_year) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_tar_re_clustmonth) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_tar_re_clustmonthyear) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")
```


###Table S4
Model summaries for Cx. quiq abundance. 
```{r}
## QUINQ
mod_abund_quin_re_none <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized, 
                       
                       vcov = "conley",
                       data = abund_quin_panel)


mod_abund_quin_re_clust <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         clust,
                       
                       vcov = "conley",
                       data = abund_quin_panel)

mod_abund_quin_re_month <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         month,
                       
                       vcov = "conley",
                       data = abund_quin_panel)


mod_abund_quin_re_year <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         year,
                       
                       vcov = "conley",
                       data = abund_quin_panel)

mod_abund_quin_re_clustmonth <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         clust + month,
                       
                       vcov = "conley",
                       data = abund_quin_panel)


mod_abund_quin_re_clustmonthyear <- feols(log(mos_per_trap_night + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized |
                         clust + month + year,
                       
                       vcov = "conley",
                       data = abund_quin_panel)



## full summaries
summary(mod_abund_quin_re_none)
summary(mod_abund_quin_re_clust)
summary(mod_abund_quin_re_month)
summary(mod_abund_quin_re_year)
summary(mod_abund_quin_re_clustmonth)
summary(mod_abund_quin_re_clustmonthyear)


## tidy summaries for supplemental table
tidy(mod_abund_quin_re_none) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_quin_re_clust) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_quin_re_month) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_quin_re_year) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_quin_re_clustmonth) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_abund_quin_re_clustmonthyear) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

```

###Table S5
Model summaries for Cx. tarsalis MIR. 
```{r}
mod_wnv_tar_re_none <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized, 
                       
                       vcov = "conley",
                       data = wnv_tar_panel)


mod_wnv_tar_re_clust <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         clust,
                       
                       vcov = "conley",
                       data = wnv_tar_panel)

mod_wnv_tar_re_month <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         month,
                       
                       vcov = "conley",
                       data = wnv_tar_panel)


mod_wnv_tar_re_year <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         year,
                       
                       vcov = "conley",
                       data = wnv_tar_panel)

mod_wnv_tar_re_clustmonth <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         clust + month,
                       
                       vcov = "conley",
                       data = wnv_tar_panel)


mod_wnv_tar_re_clustmonthyear <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         clust + month + year,
                       
                       vcov = "conley",
                       data = wnv_tar_panel)


## full summaries
summary(mod_wnv_tar_re_none)
summary(mod_wnv_tar_re_clust)
summary(mod_wnv_tar_re_month)
summary(mod_wnv_tar_re_year)
summary(mod_wnv_tar_re_clustmonth)
summary(mod_wnv_tar_re_clustmonthyear)


## tidy summaries for supplemental table
tidy(mod_wnv_tar_re_none) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_tar_re_clust) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_tar_re_month) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_tar_re_year) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_tar_re_clustmonth) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_tar_re_clustmonthyear) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

```

###Table S6
Model summaries for Cx. quinq MIR. 
```{r}
## QUINQ
mod_wnv_quin_re_none <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized, 
                       
                       vcov = "conley",
                       data = wnv_quin_panel)


mod_wnv_quin_re_clust <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         clust,
                       
                       vcov = "conley",
                       data = wnv_quin_panel)

mod_wnv_quin_re_month <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         month,
                       
                       vcov = "conley",
                       data = wnv_quin_panel)


mod_wnv_quin_re_year <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         year,
                       
                       vcov = "conley",
                       data = wnv_quin_panel)

mod_wnv_quin_re_clustmonth <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         clust + month,
                       
                       vcov = "conley",
                       data = wnv_quin_panel)


mod_wnv_quin_re_clustmonthyear <- feols(log(mir + 1) ~ 
                         pdsi_standardized_lag_1month + 
                         woy_cms_mean_standardized +
                         mean_competence_standardized |
                         clust + month + year,
                       
                       vcov = "conley",
                       data = wnv_quin_panel)


## full summaries
summary(mod_wnv_quin_re_none)
summary(mod_wnv_quin_re_clust)
summary(mod_wnv_quin_re_month)
summary(mod_wnv_quin_re_year)
summary(mod_wnv_quin_re_clustmonth)
summary(mod_wnv_quin_re_clustmonthyear)


## tidy summaries for supplemental table
tidy(mod_wnv_quin_re_none) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_quin_re_clust) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_quin_re_month) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_quin_re_year) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_quin_re_clustmonth) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

tidy(mod_wnv_quin_re_clustmonthyear) %>% mutate(across(where(is.numeric), ~ round(.x,2))) %>% filter(term != "(Intercept)")

```


###Table S7
Model summaries for Vector Index
```{r}
## Cx. tarsalis
vector_index_tar <- abund_tar_panel %>% 
  left_join(wnv_tar_panel %>% dplyr::select(clust, year, month, mir, mean_competence_standardized), by = c("clust", "year", "month")) %>% 
  mutate(vector_index = mir*mos_per_trap_night) #%>% mutate(vector_index = ((mir/1000)*mos_per_trap_night)) 
  
# hist(vector_index_tar$vector_index)
# hist(log(vector_index_tar$vector_index+1))
# range(vector_index_tar$vector_index,na.rm = TRUE) #  0.00000 37.84524

mod_vi_tar <- feols(log(vector_index + 1) ~ # log transformed better fit, 0s in data so add 1
                         pdsi_standardized_lag_1month + # primary covariate of interest
                         woy_cms_mean_standardized +
                         mean_competence_standardized | # control
                         clust + month, # fixed-effects dummy variables
                       vcov = "conley", # specify conley standard errors
                       data = vector_index_tar) # data in panel format

summary(mod_vi_tar)



## Cx. quinquefasciatus
vector_index_quin <- abund_quin_panel %>% 
  left_join(wnv_quin_panel %>% dplyr::select(clust, year, month, mir, mean_competence_standardized), by = c("clust", "year", "month")) %>% 
  mutate(vector_index = mir*mos_per_trap_night) #%>% mutate(vector_index = ((mir/1000)*mos_per_trap_night)) 

# hist(vector_index_quin$vector_index)
# hist(log(vector_index_quin$vector_index+1))
# range(vector_index_quin$vector_index,na.rm = TRUE) #  0.00000 5751.111


mod_vi_quin <- feols(log(vector_index + 1) ~ # log transformed better fit, 0s in data so add 1
                         pdsi_standardized_lag_1month + # primary covariate of interest
                         woy_cms_mean_standardized +
                        mean_competence_standardized | # control
                         clust + month, # fixed-effects dummy variables
                       vcov = "conley", # specify conley standard errors
                       data = vector_index_quin) # data in panel format

summary(mod_vi_quin)


```

